R for Clinical Study Reports and Submission

### 2021-10-27 index.Rmd
Added myself as a contributor

```{r, echo = FALSE}
contributors <- c(
  person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"),
  person("Nan", "Xiao", role = "aut"),
  person("Keaven", "Anderson", role = "aut"),
  person("Yujie", "Zhao", role = "ctr"),
  person("Aiming", "Yang", role = "ctr"),
  person("Steven", "Haesendonckx", role = "ctr")
)
```

>>>>

```{r, echo = FALSE}
contributors <- c(
  person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"),
  person("Nan", "Xiao", role = "aut"),
  person("Keaven", "Anderson", role = "aut"),
  person("Yujie", "Zhao", role = "ctr"),
  person("Aiming", "Yang", role = "ctr"),
  person("Steven", "Haesendonckx", role = "ctr"),
  person("Howard", "Baek", role = "ctr")
)
```
